Global case

### 2025-05-21 lipschitz 2025/Lipitschz.tex
update

%	However, in practice, with a reasonable timeout, this simplified model can usually obtain a better bound.
%	
	\subsection{Improving the Accuracy of the Simplified Model}
	We can improve the accuracy of the above simplified model by modifying the constraints, at the cost of increased computational time — a trade-off between accuracy and speed.

@@

>>>>

	One major disadvantage of this model is that the solution obtained through optimization may not be valid-i.e., the output computed by the network on the optimized inputs may not equal the output value in the solution. Nevertheless, it is meaningful to compute the upper bound.

%	However, in practice, with a reasonable timeout, this simplified model can usually obtain a better bound.
%	
	\subsection{Improving the Accuracy of the Simplified Model}
	We can remove the disadvantage and improve the accuracy of the above simplified model by modifying the constraints, at the cost of increased computational time — a trade-off between accuracy and speed.

@@

	This approach has a similar disadvantage as the model in previous section :the output computed by the network on the optimized inputs may not equal the output value in the solution. Similarly, it is meaningful to compute the upper bound using this approach.
